PineAPPL:\\ EW and mixed QCD--EW corrections for PDF fits

### 2020-08-03 paper/paper.tex
MOre on Sect. 3
Typos
Abstract

\usepackage[UKenglish]{babel}
\usepackage{booktabs}
\usepackage{csquotes}
\usepackage{jheppub}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{lmodern}
\usepackage[binary-units=true,detect-weight=true]{siunitx}
\usepackage{xcolor}
\usepackage[percent]{overpic}
\usepackage{mathcomp}

@@

\abstract{We introduce \textsc{PineAPPL}, a computer library that makes it possible to produce fast-interpolation 
grids for fitting parton distribution functions (PDFs)
including corrections of strong and electroweak origin. After presenting
the features and performance of such a code, we show how to interface \textsc{PineAPPL} with general-purpose
softwares that allow the user to compute such corrections, providing an explicit example with
\textsc{MadGraph5\_aMC@NLO}. We showcase some phenomenological result focusing on processes and observables
relevant for PDF fits, and 
we discuss what steps need to be undertaken in the presentation of experimental data in order to have them
consistently employed in a fit including electroweak corrections.}

>>>>

\usepackage[UKenglish]{babel}
\usepackage{booktabs}
\usepackage{csquotes}
\usepackage{jheppub}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{lmodern}
\usepackage[binary-units=true,detect-weight=true]{siunitx}
\usepackage{xcolor}
\usepackage[percent]{overpic}
\usepackage[section]{placeins}
\usepackage{mathcomp}

@@

\abstract{We introduce \textsc{PineAPPL}, a computer library that makes it possible to produce interpolation 
grids for fitting parton distribution functions (PDFs)
including corrections of strong and electroweak origin. After presenting
the features and performance of such a code, we show how to interface \textsc{PineAPPL} with general-purpose
softwares that allow the user to compute such corrections, providing an explicit example with
\textsc{MadGraph5\_aMC@NLO}. We showcase some phenomenological result focusing on processes and observables
relevant for PDF fits, and 
we discuss what steps need to be undertaken in the presentation of experimental data in order to have them
consistently employed in a fit including electroweak corrections.}
